---
title: "Latency and capacity estimation for a network connection from asymmetric measurements"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## P.1 - Analysis of the liglab2.log set
Read the data from the file and only take the date, size and time fields

```{r, include=FALSE}
library(dplyr)
library(lubridate)
library(tidyr)
```

```{r}
dt = read.table('liglab2.log', sep=' ' , na.strings = ""  , header=F , fill = TRUE)  %>% select(V1, V2, V9) 

# rename the columns to user friendly names
colnames(dt)[colnames(dt)=="V1"] <- "date"
colnames(dt)[colnames(dt)=="V2"] <- "size"
colnames(dt)[colnames(dt)=="V9"] <- "time"


```

Clean the data from any NA value
```{r}
NA_rows  = apply(dt , 1 , function(x) any(is.na(x)))
dt = dt %>% drop_na()
```

Convert times into readable values
```{r}
# define the time conversion function
convertTime = function(time)
  gsub("[^0-9.]", "", time)

# apply the previously defined function to our data
dt$time = as.numeric(sapply(dt$time , convertTime))

```


Plot the `time` values
```{r}
plot(dt$time)
```

Use `ggplot` to get a better view on the data. 
It clearly divides the data into 2 sets depending on the size of the message: set(A) < 1480 & set(B) > 1480 (not exactly 1500)
```{r}
library(ggplot2)

ggplot(data = dt, mapping = aes(x = size, y = time)) + geom_point() + theme_gray() 
```

So let's divide our sets
```{r}
# 1480 is the approximate value that splits our set into 2 subsets
sub_dt_1 = filter(dt, size < 1480)
sub_dt_2 = filter(dt, size >= 1480)
```

## Subset 1
Plot the first sub set, and zoom in to have a better look at the data (only 3 rows removed)
```{r}
library(ggplot2)
# we limit our set's max values to allow a better view of the data. (Removing a couple of rows should not impact the results)
ggplot(data = sub_dt_1, mapping = aes(x = size, y = time)) +
    geom_point() + xlim(0, 1500) + ylim(0,100)
```

### Linear regression

```{r}
ggplot(data=sub_dt_1,aes(x=size,y=time)) + theme_grey() +
    geom_point(color="black") + geom_smooth(method='lm',color="red")+ 
    coord_cartesian(ylim=c(0.9, 5))
```
Depending on the message size the minimum time seems to increase.

## Subset 2
Plot the second sub set
```{r}
ggplot(data = sub_dt_2, mapping = aes(x = size, y = time)) +
    geom_point() + xlim(1500, 2050) + theme_grey()
```

### Linear Regression
```{r}
ggplot(data=sub_dt_2,aes(x=size,y=time)) + theme_bw() +
    geom_point(color="black") +
    geom_smooth(method='lm',color="red")+ 
    coord_cartesian(ylim=c(2, 12))
```

